---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Hedge

<!-- badges: start -->
[![R-CMD-check](https://github.com/sieunyi/Hedge/workflows/R-CMD-check/badge.svg)](https://github.com/sieunyi/Hedge/actions)
[![Codecov test coverage](https://codecov.io/gh/sieunyi/Hedge/branch/main/graph/badge.svg)](https://codecov.io/gh/sieunyi/Hedge?branch=main)
<!-- badges: end -->

The goal of Hedge is to obtain optimal hedge ratios using two different methods: one is traditionally used minimum variance hedge ratio, and the other one is minimizing the semivariance hedge ratio. Based on obtained hedge ratio, the hedging effectiveness is obtained and compared.  

## Installation

You can install the released version of Hedge from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Hedge")
```

And the development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("sieunyi/Hedge")
# For installation with vignette
devtools::install_github("sieunyi/Hedge", build_vignettes = TRUE)
```

```
## Example


```{r example}
library(Hedge)

```

To properly utilize this package, you first need to import two sets of data: first column with spot price, second column with futures price that you want to calculate the hedge ratio with. Next, name this data set as x.  
```{r data}
data(fx)
spot_price = fx$...1
futures_price = fx$...2
x = cbind(spot_price, futures_price)
source('~/new folder/Hedge/R/hedge.R', echo=TRUE)
```

Finally, call the function within the package defining the window length you want to compare. 
```{r}
## basic example code
WinLen = 15
 out1 <- mvhr(x, WinLen)
 out2 <- svhr(x, WinLen) 
```

```{r pressure, echo = FALSE}
# compare hedging effectiveness
plot(out2$HE_sv, main = "Hedging effectiveness", type = 'l', col=1)
lines(out1$HE, type='l', col=3)

```
```{r}
# compare hedge ratio
plot(out2$HR_sv, type= 'l', col=1, main = "Hedge ratios")
plot(out1$HR, type='l', col=4)

```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
