---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Hedge

<!-- badges: start -->
[![R-CMD-check](https://github.com/sieunyi/Hedge/workflows/R-CMD-check/badge.svg)](https://github.com/sieunyi/Hedge/actions)
<!-- badges: end -->

The goal of Hedge is to obtain optimal hedge ratios using two different methods: one is traditionally used minimum variance hedge ratio, and the other one is minimizing the semivariance hedge ratio. Based on obtained hedge ratio, the hedging effectiveness is obtained and compared.  

## Installation

You can install the released version of Hedge from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Hedge")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sieunyi/Hedge")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Hedge)



```

To properly utilize this package, you first need to import two sets of data: first column with spot price, second column with futures price that you want to calculate the hedge ratio with. Next, name this data set as x.  
```{r data}
load("~/new folder/Hedge/data/DATAOBJECT.rda")
spot_price = DATAOBJECT$...3
futures_price = DATAOBJECT$...4
x = cbind(spot_price, futures_price)
```

Finally, call the function within the package defining the window length you want to compare. 
```{r}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
